Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-05-24 doc/paper/paper.tex
minor change
back

%\subsection{Space Invaders - v0}
%\subsubsection{Description}

%\subsubsection{Features}
%\begin{Verbatim}[fontsize=\footnotesize]
    %(A) Num[col-hv-Agent] [k=1]
    %(B) Dist[col-hv-white_king;right_col;col-hv-black_king] [k=4]
%\end{Verbatim}

%\subsubsection{Policy}
%\begin{Verbatim}[fontsize=\footnotesize]
%  1. B=0 AND A>0 -> {B INCs, A DECs}, {B NILs, A NILs}, {B INCs, A NILs}
%  2. B>0 AND A>0 -> {B DECs, A NILs}, {B NILs, A NILs}, {B INCs, A DECs}, {B NILs, A DECs}
%\end{Verbatim}

%\subsubsection{Example of Game}
%\begin{Verbatim}[fontsize=\footnotesize]

%\end{Verbatim}

@@

\subsubsection{Policy (without no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, B ↑, C ↓, D ↓}, {A ↓, B ·, C ↓, D ↓}
  2. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, B ↑, C ↓, D ↑}, {A ↑, B ·, C ↓, D ↑}
  3. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ↓, C ↓, D ↓}, {A ↑, B ↓, C ↓, D ↓}
  4. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ↑, C ↑, D ↓}
  5. A=0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ↓}, {A ↑, B ↑, C ↓, D ↓},
                                    {A ·, B ·, C ↓, D ↓}, {A ↑, B ·, C ↓, D ↓}

@@

\subsubsection{Policy (without no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
  3. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ·, C ·, D ↓}, {A ↑, B ·, C ·, D ↓}
  4. B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, B ·, C ↓, D ·}, {A ·, B ↑, C ↓, D ·}

@@

\subsubsection{Policy (without no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. C=0 AND D>0 AND B=0 AND F>0 AND A>0 -> {A ↑, B ·, C ·, D ·, E ·, F ↓},
                                            {A ·, B ·, C ·, D ·, E ·, F ↓}
  2. C=0 AND D=0 AND B=0 AND E=0 AND F=0 AND A>0 -> {A ·, B ·, C ·, D ↑, E ↑, F ·}
  3. C=0 AND D=0 AND B>0 AND E=0 AND F>0 AND A>0 -> {A ↓, B ·, C ↑, D ·, E ·, F ↓}
  4. C=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ↓}
  5. C=0 AND D=0 AND B=0 AND E=0 AND A>0 -> {A ·, B ·, C ·, D ↑, E ·, F ·}
  6. C=0 AND D=0 AND E=0 AND F>0 AND A>0 -> {A ↑, B ·, C ·, D ·, E ·, F ↓},
                                            {A ·, B ·, C ↑, D ·, E ·, F ↓},
                                            {A ↓, B ·, C ·, D ·, E ·, F ↓},
                                            {A ↑, B ·, C ↑, D ·, E ·, F ↓}
  7. C=0 AND D>0 AND B=0 AND E>0 AND F>0 AND A>0 -> {A ↓, B ·, C ·, D ·, E ·, F ↓},
                                                    {A ·, B ·, C ·, D ·, E ·, F ↓}
  8. C>0 AND D=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ·}
  9. C=0 AND D=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ↓}

@@

>>>>

\subsection{Space Invaders - v0}
\subsubsection{Description}
In this domain the agent can shoot, move to the right or to the left. To win the agent has to kill all the opponents, for this he must shoot each of them. The agent kills an opponent if he shoots while being in the same column, and he can only kill one for each shoot. The adversary has three possible actions, left, right and down, all the adversaries move in the same direction. The agent cannot be destroyed by the opponents.

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  0: Num[cell-has-martian] [k=1]
	1: Num[cell-has-target_martian] [k=1]
	2: Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]]
\end{Verbatim}

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. C=0 AND A>0 AND B>0 -> {A ↓, B ↑, C ↑}, {A ·, B ↓, C ·}, {A ↓, B ·, C ↑}
  2. C=0 AND A=0 AND B>0 -> {A ·, B ↓, C ↑}
  3. C>0 AND B>0 -> {A ·, B ·, C ↓}
  4. C>0 AND A=0 AND B>0 -> {A ·, B ·, C ↓}
\end{Verbatim}

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]

@@

\subsubsection{Policy (with no fixed action space)}

\begin{Verbatim}[fontsize=\footnotesize]
  1. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, B ↑, C ↓, D ↓}, {A ↓, B ·, C ↓, D ↓}
  2. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, B ↑, C ↓, D ↑}, {A ↑, B ·, C ↓, D ↑}
  3. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ↓, C ↓, D ↓}, {A ↑, B ↓, C ↓, D ↓}
  4. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ↑, C ↑, D ↓}
  5. A=0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ↓}, {A ↑, B ↑, C ↓, D ↓},
                                    {A ·, B ·, C ↓, D ↓}, {A ↑, B ·, C ↓, D ↓}

@@

\subsubsection{Policy (with no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
  3. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ·, C ·, D ↓}, {A ↑, B ·, C ·, D ↓}
  4. B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, B ·, C ↓, D ·}, {A ·, B ↑, C ↓, D ·}

@@

\subsubsection{Policy (with no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. C=0 AND D>0 AND B=0 AND F>0 AND A>0 -> {A ↑, B ·, C ·, D ·, E ·, F ↓},
                                            {A ·, B ·, C ·, D ·, E ·, F ↓}
  2. C=0 AND D=0 AND B=0 AND E=0 AND F=0 AND A>0 -> {A ·, B ·, C ·, D ↑, E ↑, F ·}
  3. C=0 AND D=0 AND B>0 AND E=0 AND F>0 AND A>0 -> {A ↓, B ·, C ↑, D ·, E ·, F ↓}
  4. C=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ↓}
  5. C=0 AND D=0 AND B=0 AND E=0 AND A>0 -> {A ·, B ·, C ·, D ↑, E ·, F ·}
  6. C=0 AND D=0 AND E=0 AND F>0 AND A>0 -> {A ↑, B ·, C ·, D ·, E ·, F ↓},
                                            {A ·, B ·, C ↑, D ·, E ·, F ↓},
                                            {A ↓, B ·, C ·, D ·, E ·, F ↓},
                                            {A ↑, B ·, C ↑, D ·, E ·, F ↓}
  7. C=0 AND D>0 AND B=0 AND E>0 AND F>0 AND A>0 -> {A ↓, B ·, C ·, D ·, E ·, F ↓},
                                                    {A ·, B ·, C ·, D ·, E ·, F ↓}
  8. C>0 AND D=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ·}
  9. C=0 AND D=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ↓}

@@

\subsubsection{Action space}
\begin{Verbatim}[fontsize=\footnotesize]
UP = 0
DOWN = 1
RIGHT = 2
LEFT = 3
\end{Verbatim}
